\ttlfnt{Comparing the performance of websites and their content distribution networks}

### 2016-08-26 Writeup/paper.tex
Added some comments

% TODOs:
% 	- add a section on the tool, what it does and how it tries to ensure accuracy and repeatability in our dynamic environment (throughput and ping tests beforehand, repeating each run 3 times, re-try logic to make the code robust etc. etc. Just sell it!)
% 	- (Sub?)Section on the data we collect and why this information is useful for our study
\section{Method}\label{sec:method}
\subsection{Measurement and tools}
To measure the performance of CDNs, we have created a tool to automatically capture various quantitative and qualitative performance metrics when given a list of URLs to online video or audio content. In order to compare the performance of CDNs to that of the websites that present the content, we measure 2 primary quantitative metrics: Ping or Round-trip-time and the number of hops required to reach the server. We also measure the throughput to the CDN. To gain further insight into the potential causes for variances in performance, we also take note of the location and owner of the web page and CDN IPs.

@@

For each input URL we run youtube-dl and ask that it simply return the URL of the actual content and exit. Both URLs are resolved to IP addresses and stored for later measurement. We then run tcpdump, specifying that it will terminate after 3000 packets have been received, and then run youtube-dl again. This time we let youtube-dl actually download the media file, allowing tcpdump to the required 3000 packets and then terminate. At this point we can kill the youtube-dl process and just consider its output. First, we look at the last line of output from youtube-dl in order to get the throughput that the content was transmitted at. This does mean that we rely on youtube-dl's measurements being accurate, but previous attempts to measure throughput ourselves proved inaccurate as youtube-dl does some work before downloading (for example to get the CDN URL from the webpage).

@@

\section{Results}\label{sec:results}
\subsection{Home network}
We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929}.
Below are the results of each run, averaged across ISPs:
\vspace{1em} \\
Ping: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 39  & 35  & 56  \\ \hline
  & Popular Youtube   & 60  & 14  & 14  \\ \hline
  & Soundcloud        & 161 & 162 & 184 \\ \hline
  & Twitch.tv         & 198 & 159 & 172 \\ \hline
2 & Unpopular Youtube & 45  & 14  & 17  \\ \hline
  & Popular Youtube   & 63  & 14  & 31  \\ \hline
  & Soundcloud        & 161 & 160 & 165 \\ \hline
  & Twitch.tv         & 193 & 159 & 181 \\ \hline
3 & Unpopular Youtube & 31  & 17  & 14  \\ \hline
  & Popular Youtube   & 31  & 23  & 18  \\ \hline
  & Soundcloud        & 179 & 171 & 160 \\ \hline
  & Twitch.tv         & 184 & 159 & 161 \\ \hline
\end{tabular}
\vspace{1em} \\
Number of hops: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 10 & 7  & 10 \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 14 & 14 & 15 \\ \hline
2 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 13 & 15 & 12 \\ \hline
3 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 13 & 15 & 13 \\ \hline
\end{tabular}
\vspace{1em} \\
Throughput (KB/s): \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Content \\ \hline
1 & Unpopular Youtube & 197.8 \\ \hline
  & Popular Youtube   & 202.6 \\ \hline
  & Soundcloud        & 197.9 \\ \hline
  & Twitch.tv         & 201.2 \\ \hline
2 & Unpopular Youtube & 201.9 \\ \hline
  & Popular Youtube   & 197.8 \\ \hline
  & Soundcloud        & 201.3 \\ \hline
  & Twitch.tv         & 203.1 \\ \hline
3 & Unpopular Youtube & 202.8 \\ \hline
  & Popular Youtube   & 200.4 \\ \hline
  & Soundcloud        & 203.6 \\ \hline
  & Twitch.tv         & 204.9 \\ \hline
\end{tabular}

>>>>

% TODOs:
% 	- add a section on the tool, what it does and how it tries to ensure accuracy and repeatability in our dynamic environment (throughput and ping tests beforehand, repeating each run 3 times, re-try logic to make the code robust etc. etc. Just sell it!)
% 	- (Sub?)Section on the data we collect and why this information is useful for our study
\section{Method}\label{sec:method}
\subsection{Measurement and tools}
% Possible improvements / modifications:
% "owner of the web page" -> organisation hosting the webpage?
% Why 3000 packets?
% We also do a ping test at the start to ensure that latency is in a reasonable range (< 150 ms)
%
%

To measure the performance of CDNs, we have created a tool to automatically capture various quantitative and qualitative performance metrics when given a list of URLs to online video or audio content. In order to compare the performance of CDNs to that of the websites that present the content, we measure 2 primary quantitative metrics: Ping or Round-trip-time and the number of hops required to reach the server. We also measure the throughput to the CDN. To gain further insight into the potential causes for variances in performance, we also take note of the location and owner of the web page and CDN IPs.

@@

For each input URL we run youtube-dl and ask that it simply return the URL of the actual content and exit. Both URLs are resolved to IP addresses and stored for later measurement. We then run tcpdump, specifying that it will terminate after 3000 packets have been received, and then run youtube-dl again. This time we let youtube-dl actually download the media file, allowing tcpdump to capture the required 3000 packets and then terminate. At this point we can kill the youtube-dl process and just consider its output. First, we look at the last line of output from youtube-dl in order to get the throughput that the content was transmitted at. This does mean that we rely on youtube-dl's measurements being accurate, but previous attempts to measure throughput ourselves proved inaccurate as youtube-dl does some work before downloading (for example to get the CDN URL from the webpage).

@@

\section{Results}\label{sec:results}
\subsection{Home network}
% We are missing the caching train in this section wrt unpopular video (since the same video is used)
% Telkom is first -> EU -> Telkom -> Telkom
% Then ISP 2 is second -> Google Cache -> ISP 2 -> ISP 2
% Then ISP 3 is third -> Google Cache -> ISP 3 -> ISP 3
% Then ISP 4 is fourth but uses same backbone as ISP 3 so -> ISP 3 -> ISP 3 -> ISP 3 etc.

We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929}.
Below are the results of each run, averaged across ISPs:
\vspace{1em} \\
Ping: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 39  & 35  & 56  \\ \hline
  & Popular Youtube   & 60  & 14  & 14  \\ \hline
  & Soundcloud        & 161 & 162 & 184 \\ \hline
  & Twitch.tv         & 198 & 159 & 172 \\ \hline
2 & Unpopular Youtube & 45  & 14  & 17  \\ \hline
  & Popular Youtube   & 63  & 14  & 31  \\ \hline
  & Soundcloud        & 161 & 160 & 165 \\ \hline
  & Twitch.tv         & 193 & 159 & 181 \\ \hline
3 & Unpopular Youtube & 31  & 17  & 14  \\ \hline
  & Popular Youtube   & 31  & 23  & 18  \\ \hline
  & Soundcloud        & 179 & 171 & 160 \\ \hline
  & Twitch.tv         & 184 & 159 & 161 \\ \hline
\end{tabular}
\vspace{1em} \\
Number of hops: \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Website & CDN & Content \\ \hline
1 & Unpopular Youtube & 10 & 7  & 10 \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 14 & 14 & 15 \\ \hline
2 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 13 & 15 & 12 \\ \hline
3 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
  & Popular Youtube   & 10 & 8  & 8  \\ \hline
  & Soundcloud        & 13 & 18 & 18 \\ \hline
  & Twitch.tv         & 13 & 15 & 13 \\ \hline
\end{tabular}
\vspace{1em} \\
Throughput (KB/s): \\
\begin{tabular}{|l|l|c|c|c|} \hline
Run & Source & Content \\ \hline
1 & Unpopular Youtube & 197.8 \\ \hline
  & Popular Youtube   & 202.6 \\ \hline
  & Soundcloud        & 197.9 \\ \hline
  & Twitch.tv         & 201.2 \\ \hline
2 & Unpopular Youtube & 201.9 \\ \hline
  & Popular Youtube   & 197.8 \\ \hline
  & Soundcloud        & 201.3 \\ \hline
  & Twitch.tv         & 203.1 \\ \hline
3 & Unpopular Youtube & 202.8 \\ \hline
  & Popular Youtube   & 200.4 \\ \hline
  & Soundcloud        & 203.6 \\ \hline
  & Twitch.tv         & 204.9 \\ \hline
\end{tabular}
